---
title: "Assignment 7 Dynamic Report"
author: "Santiago Charry"
format: html
editor: visual
---

```{r include=FALSE}
#| echo: false
#Library loading and data setup
library(tidyverse)
library(data.table) ## For the fread function
library(lubridate)

source("sepsis_monitor_functions.R")

library(googledrive)
library(gt)

drive_deauth()
file_link <- "https://drive.google.com/file/d/1KFeLNJIPAc8oCrmZDsRNR6yjdru01xpp/view?usp=share_link"

## All data up until now
new_data <- updateData(file_link)

## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))
```

## This report was created at `r Sys.time()`

## Table of All Patients Vital Changes in Their Latest Hour

Change in vitals over each patient's latest hour.

```{r, echo = FALSE}
#| echo: false 
new_data <- updateData(file_link)

# Subsetting the latest two observations for each subject using ICULOS
last_two_obs_by_patient <- new_data %>%
  group_by(PatientID) %>%
  arrange(desc(ICULOS)) %>%
  slice(1:2)

# Calculating change in vitals
change_in_vitals <- last_two_obs_by_patient %>%
  group_by(PatientID) %>%
  summarize(
    HR_Change = HR[2] - HR[1],
    Temp_Change = Temp[2] - Temp[1],
    Resp_Change = Resp[2] - Resp[1]
  )

gt(change_in_vitals)

```

## Table of Current Sepsis Patients + Vitals

Patients who currently have sepsis along with current heart rate, temperature, and respiratory rate.

```{r, echo = FALSE}
#| echo: false

septic_patients <- most_recent_data %>%
  group_by(PatientID) %>%
  filter(SepsisLabel == 1) %>%
  summarize(HR, Temp, Resp)

gt(septic_patients)

```

## Plots for septic patients with history of vitals

Spaghetti plots depicting change in vitals for septic patients throughout their stay at the ICU (in hours). 

```{r, echo = FALSE}
#| echo: false
new_data %>%
  filter(SepsisLabel == 1) %>%
  ggplot(aes(x = ICULOS, y = HR, color = PatientID)) +
    geom_line() +
    labs(x = "ICU Length of Stay", y = "Heart Rate", title = "Spaghetti Plot for Heart Rate")

new_data %>%
  filter(SepsisLabel == 1) %>%
  ggplot(aes(x = ICULOS, y = Temp, color = PatientID)) +
    geom_line() +
    labs(x = "ICU Length of Stay", y = "Temperature", title = "Spaghetti Plot for Temperature")

new_data %>%
  filter(SepsisLabel == 1) %>%
  ggplot(aes(x = ICULOS, y = Resp, color = PatientID)) +
    geom_line() +
    labs(x = "ICU Length of Stay", y = "Respiratory Rate", title = "Spaghetti Plot for Respiratory Rate")
```
